Draft Final Report: Measles risk assessment, modelling, and benefit--cost analyses for New Zealand

### 2015-06-12 draftfinalreport_v4.Rnw
MMR1 was at 15 months not 12

\begin{figure}
\begin{center}
     \includegraphics[width=0.9\textwidth]{vacc_age.pdf}
\end{center}
\caption{Age of vaccination of vaccinated measles cases, 2007--12~June~2014. Recommended vaccination age in months is shown for the measles, mumps, rubella (MMR) dose 1 (12 months) and MMR dose 2 (4 years). See \autoref{fig:vaccstat_close} for details}
\label{fig:vaccstat}
\end{figure}

\begin{figure}
\begin{center}
     \includegraphics[width=0.9\textwidth]{vacc_age_close.pdf}
\end{center}
\caption{Age of vaccination of vaccinated measles cases, 2007--12~June~2014 in details. Recommended vaccination age in months is shown for the measles, mumps, rubella (MMR) dose 1 (12 months) and MMR dose 2 (4 years)}
\label{fig:vaccstat_close}
\end{figure}

>>>>

\begin{figure}
\begin{center}
     \includegraphics[width=0.9\textwidth]{vacc_age.pdf}
\end{center}
\caption{Age of vaccination of vaccinated measles cases, 2007--12~June~2014. Recommended vaccination age in months is shown for the measles, mumps, rubella (MMR) dose 1 (15 months) and MMR dose 2 (4 years). See \autoref{fig:vaccstat_close} for details}
\label{fig:vaccstat}
\end{figure}

\begin{figure}
\begin{center}
     \includegraphics[width=0.9\textwidth]{vacc_age_close.pdf}
\end{center}
\caption{Age of vaccination of vaccinated measles cases, 2007--12~June~2014 in details. Recommended vaccination age in months is shown for the measles, mumps, rubella (MMR) dose 1 (15 months) and MMR dose 2 (4 years)}
\label{fig:vaccstat_close}
\end{figure}
